\speculake: Hiding Malware in Speculative Execution

### 2018-12-13 paper/figures.tex
table pass

\newcommand{\processorTable}{
\begin{table}
    \centering
    % \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{X X X| Y Y Y}
    \begin{tabularx}{\linewidth}{X b b| Y Y Y}
        \ \newline
        \ \newline
        Processor & \ \newline
        Year\newline
        released & \ \newline
        Micro\newline
        arch & \ \newline
        Nested\newline 
        Spec? & Num\newline
        indirect jumps* & Max $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & 26 & 178\\
        AMD EPYC 7251             & 2017 & Ryzen   &            & 4  & 178\\
        \\
    \end{tabularx}%}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on one AMD and three Intel processors. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}) though
    the older Haswell processor and the AMD processor were not. We found that
    the Intel Xeon CPU E3-1270 v6 required 28 identical indirect jumps in the
    trigger and payload programs to reliably enter the speculative world at the
    desired speculative entry point ($> 95\%$) while the Intel Core i5-7200U
    and Intel Xeon CPU E3-1276 v3 only required 26 jumps. The AMD EPYC 7251
    processor maintained a 85\% speculative hit rate with as low as 4 and as
    high as 32 training jumps.}
    \label{table:processors}
\end{table}
}

>>>>

\newcommand{\processorTable}{
\begin{table}
    \centering
    % \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{X X X| Y Y Y}
    \begin{tabularx}{\linewidth}{X b b| Y Y Y}
        \toprule
        \ \newline
        Processor &
        %Year\newline
        \ \newline
        Released &
        Micro- %\newline
        arch. & Nested\newline 
        Spec. &
        Indirect jumps & $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & 26 & 178\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        AMD EPYC 7251             & 2017 & Ryzen   &            & 4  & 178\\
        \toprule
    \end{tabularx}%}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel processors and one AMD. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}).
    Indirect jumps is the number of common training indirect jumps needed
    in the trigger program to reliably ($ > 95\%$ of the time) coerce the
    payload program to follow the pattern and jump to the speculative entry
    point specified in the trigger program. $\mu$~ops is the upper bound
    of $\mu$~ops that can be performed speculatively.}

    \label{table:processors}
\end{table}
}
